---
title: "Semi-automated rapid evidence mapping"
author: "Liz Law, Matt Grainger"
date: "11/9/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# Semi-automated rapid evidence mapping
Example: mapping the evidence for impacts of managed bees on native bees


## Searching the literature

The problem

- Complex search terms (AND, OR, NEAR…TOPICS, TITLES, TYPES… SOURCES, YEARS…)
- Unknown search terms (familiar with only part of the literature)
- Getting too much/not enough literature

*add examples here 

## Two solutions

litsearchr :: semi automated search terms
scimeetr / bibiometrix :: group/characterise the literature

## litsearchr 

- partially automates keyword selection and writing Boolean search strings
- uses the Rapid Automatic Keyword Extraction algorithm to identify potential keywords from a scoping search 
- selects important keywords based on their importance in a keyword co-occurrence network
- after keywords are grouped into concept groups, litsearchr writes Boolean searches

- caveats??

## litsearchr example

* add example here

## scimeetr 

Designed to "help explore the literature" by

- characterising literature communities by keywords (title, abstract, keywords, keywords+, and cited references)
- return tags, top keywords, authors, cited literature
- generate reading lists by ranking, OR bibiography network characteristics

- caveats: only on github, 'beta' version

## scimeetr example

* add example here

## Diving deeper

doi2text

- automates finding of full text 
- identifies sections

text mining of (primary) literature

- e.g.
- searching for specific terms within the methods/results text 
  - species / species types 
  - landscapes / locations
  - sampling methods (pan, malaise, netting, etc)
- searching for data in figures and tables through legends
  
- caveat(?) 
  - needs to be fed in 'lists' 
  - but this useful for standardisation of the literature
  - we can potentially automate creation of these lists via text mining

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

